### 2023-11-08 manuscript.tex
Added missing reference to substitution panels E-F

To highlight the differences in patterns of residue substitution between the disorder and order regions, the parameters in each model are directly compared in Fig.~\ref{fig:substitution}, beginning with the frequency vectors. The disorder regions show an enrichment of ``disorder-promoting'' residues such as serine, proline, and alanine, and a depletion of hydrophobic and bulky residues such as trytophan and phenylalanine (Fig.~\ref{fig:substitution}A). The exchangeability matrices fit to the disorder and order regions have similar overall patterns of high and low coefficients (Fig.~\ref{fig:substitution}B-C). However, the log ratios of the disorder to the order exchangeability coefficients show clear differences within and between the disorder-enriched and -depleted residues. The disorder-enriched residues are less exchangeable with each other, whereas disorder-depleted residues are more exchangeable with each other and with disorder-enriched residues (Fig.~\ref{fig:substitution}D). Likewise, we observe a trend in the log ratios of the rate coefficients where the coefficients above the diagonal are generally positive, and those below the diagonal are generally negative. As the coefficients model the one-way rates of substitution between residues with the vertical and horizontal axes indicating the initial and target residues, respectively, this suggests a net flux towards a more disorder-like composition. However, the coefficients between the disorder-depleted and -enriched classes of residues for both the exchangeability and rate matrices should be interpreted with caution, as they are estimated with a high amount of uncertainty (Fig.~\ref{sfig:CV_ematrix}-\ref{sfig:CV_rmatrix}).

>>>>

To highlight the differences in patterns of residue substitution between the disorder and order regions, the parameters in each model are directly compared in Fig.~\ref{fig:substitution}, beginning with the frequency vectors. The disorder regions show an enrichment of ``disorder-promoting'' residues such as serine, proline, and alanine, and a depletion of hydrophobic and bulky residues such as trytophan and phenylalanine (Fig.~\ref{fig:substitution}A). The exchangeability matrices fit to the disorder and order regions have similar overall patterns of high and low coefficients (Fig.~\ref{fig:substitution}B-C). However, the log ratios of the disorder to the order exchangeability coefficients show clear differences within and between the disorder-enriched and -depleted residues. The disorder-enriched residues are less exchangeable with each other, whereas disorder-depleted residues are more exchangeable with each other and with disorder-enriched residues (Fig.~\ref{fig:substitution}D). Likewise, we observe a trend in the log ratios of the rate coefficients where the coefficients above the diagonal are generally positive, and those below the diagonal are generally negative (Fig.~\ref{fig:substitution}E-F). As the coefficients model the one-way rates of substitution between residues with the vertical and horizontal axes indicating the initial and target residues, respectively, this suggests a net flux towards a more disorder-like composition. However, the coefficients between the disorder-depleted and -enriched classes of residues for both the exchangeability and rate matrices should be interpreted with caution, as they are estimated with a high amount of uncertainty (Fig.~\ref{sfig:CV_ematrix}-\ref{sfig:CV_rmatrix}).
